Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-14 latex/comp_or.tex
OptCGcons and Shims updated
Paper updated

{\color{blue}
Figure \ref{fig:whip} represents the $n_{\pi(k)}$\/ possible edges $e_{ij}^{\pi(k)}$\/ of $p_i$\/ sorted by $\theta_{ij}^{\pi(k)}$. \emph{Shims}\/ starts with a greedy solution, stopping at the edge with index in $\eta_1[i]$ close to the local optimum (first phase). Then, considering even the edge with the index $\eta_2[i]$, it elaborates different possible complements for this pallet and selects the best of these complements (second phase).

Although the second phase solves a knapsack problem, an algorithm for solving a bin packing problem was used (the First Fit Decreasing - FFD), and the most profitable bin (shims) was selected. This method was proved to be faster than a dynamic program solution for the knapsack problem.

@@

$1^{st}$ - Greedy phase with torque surplus

$2^{st}$ - Minimization of CG deviation

$3^{st}$ - {\it Shims} construction and best {\it Shims} selection

All executed in a multi-process runtime, accessing concurrently, reading and writing, the list of items and the current value of the CG deviation.

As to the multi-process runtime, we considered each pallet as a process.
}

@@

Line \ref{mpShims:minCGdev} calls the $minCGdev$ method which updates the $nodeTorque$ and $G$. $minCGdev$ minimizes the CG deviation and repairs the greedy solution if it is infeasible.

@@

\subsubsection{{\it Shims} second phase: improvement on minimizing CG deviation}

Between the greedy and the {\it Shims} selection phases we inserted, in this work, a method to minimize the CG deviation, as stated by the model that follows.

@@

@@

{\it mpShims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, mpShims was 2.6 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the run-time {\it race condition} management limited {\it mpShims} performance.

@@

@@

{\it surplus} & {\bf Scenario} & {\bf Before (m)} & {\bf After (m)}  & {\bf Improvement (\%)}  \\
\midrule
\multirow{6}{*}{$1.2$}& 1 &  33  &  16 & 52\\
&                       2 & 194  & 154 & 21\\
&                       3 & 149  & 119 & 20 \\
&                       4 & 135  & 103 & 23 \\
&                       5 & 121  &  84 & 31 \\
&                       6 & 105  &  71 & 33 \\
\midrule
\multirow{6}{*}{$1.5$}& 1 &  32 &  18 & 44 \\
&                       2 & 198 & 135 & 32 \\
&                       3 & 156 & 128 & 18 \\
&                       4 & 137 & 106 & 22\\
&                       5 & 120 &  87 & 28 \\
&                       6 & 106 &  77 & 27 \\
\midrule
\multirow{6}{*}{$2.0$}& 1 &  33 &  20 & 38 \\
&                       2 & 199 & 142 & 28 \\
&                       3 & 156 & 122 & 22 \\
&                       4 & 138 & 106 & 23 \\
&                       5 & 123 &  84 & 31 \\
&                       6 & 109 &  75 & 31 \\
\midrule
&                         &        & {\bf Average} & {\bf 29}\\
\bottomrule	
\end{tabular}
%\textsuperscript{asdf sd .}	
\normalsize
\end{table}

>>>>

Figure \ref{fig:whip} represents the $n_{\pi(k)}$\/ possible edges $e_{ij}^{\pi(k)}$\/ of $p_i$\/ sorted by $\theta_{ij}^{\pi(k)}$. \emph{Shims}\/ starts with a greedy solution, stopping at the edge with index in $\eta_1[i]$ close to the local optimum (first phase). Then, considering even the edge with the index $\eta_2[i]$, it elaborates different possible complements for this pallet and selects the best of these complements (second phase).

Although the second phase solves a knapsack problem, an algorithm for solving a Bin Packing Problem was used (the First Fit Decreasing - FFD), and the most profitable bin (Shims) was selected. This method was proved to be faster than a Dynamic Program solution for the Knapsack Problem.

@@

$1^{st}$ - A Greedy phase to partially build pallets.

$2^{st}$ - Minimization of CG deviation.

$3^{st}$ - {\it Shims} set construction and best {\it Shims} selection

All executed in a multi-process execution, accessing concurrently, reading and writing, the list of items and the current value of the CG deviation.
As to the multi-process execution, we considered each pallet as a process.

@@

Line \ref{mpShims:minCGdev} calls the $minCGdev$ integer programming method (Subsection \ref{subsection:second_phase}) which updates the $nodeTorque$ and $G$. $minCGdev$ minimizes the CG deviation. We raise the hypothesis that, in sequential mode, where one pallet is built at a time, torque constraints may be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. So, we decided to balance cargo before the next {\it Shims} phase to allow more room for pallet fulfillment. This will be confirmed (or not) in Section \ref{sec6}.

@@

\subsubsection{{\it Shims} second phase: improvement on minimizing CG deviation}
\label{subsection:second_phase}

Between the greedy and the {\it Shims} selection phases we inserted, in this work, an integer programming method to minimize the CG deviation, as stated by the model that follows.

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results}  \label{tab:results2}
	\footnotesize
	%\scriptsize
	\begin{tabular}{crcccccccc}
		\toprule
		{\bf Volume}     &  {\bf Resolution}   &                              &\multicolumn{6}{c}{\bf Scenarios}                                                   &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\it surplus}    & {\it method}        & {\bf Results}                &{\bf 1}      &{\bf 2}      &{\bf 3}      &{\bf 4}      &{\bf 5}       &{\bf 6}      &{\bf Speedup} \\
		\toprule

		\multirow{6}{*}{$1.2$}&\specialcell{$Relaxed$\\$Gurobi$}& $f$         &{\it 12.02}   &{\it 8.74}   &{\it 12.56} &{\it 14.34}  &{\it 14.79}   &{\it 13.49}       & 1.00 \\%

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &  10.34       & 8.50        & 12.42      &  15.06      &  15.97       &  15.88       &   \\% 
		&                                                & {\it run time (s)} &  < 1         &  3          &  5         &   20        &  58          &  352         &  1.0 \\%

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &  11.76       &  8.57       & 12.28      &  14.02      &  14.50       & 13.23        & \\%

		&                                                & {\it run time (s)} &  < 1         &  2          &  3         &   47        &  33          & 193         &  {\bf 2.8}\\%

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &         &         &       &        &        &         &  \\%8633
		&                                                & {\it run time (s)} &  < 1         &  4          &    7        &   26        &   81        &  520         & 1.0\\% 639

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &         &        &        &  &        &         & \\%9721
		&                                                & {\it run time (s)} &  < 1         &  2          &    3        &    12       &   38        &   236        & {\bf 2.2}\\% 292

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $Shims$}                       & $f$                &         &        &        &        &        &         & \\% 12767
		&                                                & {\it run time (s)} &  2           &  9          &    17       &   68        &   206       &  1216        & 1.0\\% 1518

		\cmidrule{2-10}		                       
		&\multirow{2}{*}{ $mpShims$}                     & $f$                &         &        &        &        &        &         &  \\% 13377
		&                                                & {\it run time (s)} &  2           &  3          &    5        &   20        &   64        &  398         & {\bf 2.8}\\% 544

@@

{\it mpShims} had a quality performance very close to the {\it Relaxed Gurobi} upper bound solution, and, as to the {\bf Speedup}, on average, mpShims was 2.6 times faster than {\it Shims}. Theoretically, it could be more, but due to the burden of sharing the CG deviation and the list of items among the processes (pallets) for reading and writing, the execution {\it race condition} management limited {\it mpShims} performance.

@@

We confirmed the hypothesis raised in line \ref{mpShims:minCGdev} of Algorithm \ref{alg:mpShims} that, in sequential mode, where one pallet is built at a time, torque constraints could be more restrictive than volume or weight constraints, which could stop the palletization process earlier, fostering a solution that may be not as good as it could be. This integer programming procedure inclusion really improved {\it Shims} results.

@@

{\it surplus} & {\bf Scenario} & {\bf Before (m)} & {\bf After (m)}  & {\bf Improvement (\%)}  \\
\midrule
\multirow{6}{*}{$1.2$}& 1 &  32 &  32 & 0.0 \\
&                       2 & 181 & 181 & 0.0 \\
&                       3 & 149 & 149 & 0.0\\
&                       4 & 131 & 131 & 0.0  \\
&                       5 & 113 & 113 & 0.0  \\
&                       6 & 105 & 105 & 0.0 \\
\midrule
\multirow{6}{*}{$1.5$}& 1 &  &  &  \\
&                       2 &  &  &  \\
&                       3 &  &  &  \\
&                       4 & 123 & 92 & 25.3  \\
&                       5 &  &  &  \\
&                       6 &  &  &  \\
\midrule
\multirow{6}{*}{$2.0$}& 1 &  &  &  \\
&                       2 &  &  &  \\
&                       3 &  &  &  \\
&                       4 &  &  &  \\
&                       5 &  &  &  \\
&                       6 &  &  &  \\
\midrule
&                         &        & {\bf Average} & {\bf 29}\\
\bottomrule	
\end{tabular}
%\textsuperscript{asdf sd .}	
\normalsize
\end{table}
